Crowdy: Social Crowd Visualization

### 2011-04-28 docs/crowdy_gui.tex
add snapshot and future work to the report

This section illustrate an outline of the prototype. We want to provide
the user with a simple and flexible interface to maximize their options for
exploring while minimizing their memory overhead. Existing web applications
show that the most general task should be the main focus and the other
available options may be placed on the side or hidden according to their
frequency of usage. Since the primary function of our system is to visualize
the Crowds emerged over time, the crowd display window is our
first priority. In the crowd display window, we
consider the needs of personalization for our potential users(e.g. Analyst).
There is a global view panel and a personal workspace panel. The personal
workspace panel distinguishes from the global view panel in a way that it only
shows the set of crowds marked by the user when exploring in the global view
panel. We have tabs to help our users quickly and easily transit between these
two views. Inside each view, we need to decide the best format to condense
a massive amount of data. Each crowd has metadata associated with it such as
starting and ending time, crowd participants, topics, tweets,
location data, etc. To effectively organize these properties to assist quick
and convenient retrieval by the user, we consider these two formats: timeline
and list. For both view panels, these two formats are included but sized
unequally. The size is adjustable(in the option panel) according to the user's
need. Generally, ``timeline'' is more suitable for overview a large number of
crowds while ``list'' is better for investigating details in a smaller set of crowds. We
also provide several filtering options for both timeline and list format in the
option panel. Some detailed components in these three panels are listed below.

\begin{itemize}
    \item \textit{Global View Panel} : The global view shows the global crowds
    in different format. When a crowded is marked by the user, a flag will be
    placed in front of each crowd item in each format.

    \begin{itemize}
        \item Timeline format displays the evolution of each crowd.
        First of all, a crowd is shown as a line from the starting time
        to the ending time. The size of the participants over time is
        indicated by color(e.g., small-large-medium $\longrightarrow$
        green-red-blue). The top three keywords that describe the topic of
        the crowd are displayed explicitly on the timeline along with
        the crowd line. Extra information about the crowd can be viewed
        in the pop up box when the user clicks on the crowd line.
        \item List format displays each crowd with some specific
        sorting order. The default sorting order is by the starting
        time. Some other available sorting functions include the
        ending time, the size of crowds and the ranging time. In the
        list format, crowds are displayed explicitly in three columns:
        time period, keywords and some of the participants. The latter
        two columns are clickable. After clicked, it will show the list
        of tweets and the full set of participants in a pop up window
        form.
    \end{itemize}

    \item \textit{Personal Workspace Panel} : Similar as the Global View Panel
    but with only the set of crowds marked by the user in the Global View
    Panel.
    \item \textit{Filter Option Panel} : This panel explicitly displays a set of
    the most frequently used filtering options such as search and timeline scaling.
    We also provide the user with flexibility to adjust the default
    settings we provided such as the primary display format in the View
    Panel, list sorting function and time period filtering. Other filtering
    options are hidden and can be expanded with a click on the right bottom corner
    of the Panel.
\end{itemize}

@@

We apply the Simile Timeline library which is developed by MIT's Computer
Science and Artificial Intelligence Laboratory. The timeline shows all of the
crowds at a given time span.  The timeline allows the analyist to zoom in on a
specific time, and move forward and backward thorough time.  The visualization
shows how long the crowd lasts, and the size of the crowd. We may make the
crowd taller or shorter based on the size of the crowd.  We will also display a
few keywords from each crowd.

@@

The list view requires a dynamic table in which it displays as many rows as the
amount of crowds returned by the API. Concretely, we issue a jQuery for all the
available crowds in the database. The javascript helps to create the dynamic
table which includes the following columns: Like, Period and number of users in the crowd. Users can click on the ``like'' of each crowd to indicate the preference. The preferred crowds will be push up to the beginning of the list. Once a row of crowd is clicked, a slide down box with detail information(crowd user network, tweets) will be shown below. In order to provide users a cleaner page view, we restrict 5 tweets per page to show in the slide down box and thus, a multiple page navigation is possible.
Each crowd has a star-feature attached to it which can be used by the user to mark his favourite crowds.This feature is present in the detailed view of the crowd which is activated as said earlier by selecting the row of a crowd.This is used to rearrange the list of crowds with the starred crowds appearing at the top whenever the user comes back to the list view.The user can mark any crowd as starred or unstar the ones that are already starred at any point of time.

@@

In the search function of the system, we provide a main search box in which 
users can type a textual query to search for crowds which contains the query.
Besides, users can also click the link of advanced search, so that they can 
choose options of words, time period of crowd, size of crowd, presentation ways,
and results they would like to see per page. We maintain indices for each kind
of queries in the MongoDB database, so that we can efficiently return the results
to users. Whenever a query is issued, the systems send a HTTP GET request to the
backend, and the server would return the corresponding search results.

@@

\subsubsection{Crowd View}
When an analyst clicks a crowd in the list, timeline, or map view, we show an
expanded view of the crowd. This is a form of progressive disclosure, where we
give the analyst more information as they need it.  At the moment, we just show
a network graph where nodes represent users, and edges represent the tweets
between users. We plan to add the ability to drill down even more.  When the
analyst clicks on a node, we can give the analyst more information about the
user that was clicked on. When the analyst clicks on an edge, we can show the
conversation between two users.

@@

>>>>

This section illustrate an outline of the prototype. We want to provide
the user with a simple and flexible interface to maximize their options for
exploring while minimizing their memory overhead. Existing web applications
show that the most general task should be the main focus and the other
available options may be placed on the side or hidden according to their
frequency of usage. Since the primary function of our system is to visualize
the Crowds emerged over time, the crowd display window is our
first priority. In the crowd display window, we
consider the needs of personalization for our potential users(e.g. Analyst).
There is a global view panel and a personal workspace panel. The personal
workspace panel distinguishes from the global view panel in a way that it only
shows the set of crowds marked by the user when exploring in the global view
panel. Inside each view, we need to decide the best format to condense
a massive amount of data. Each crowd has metadata associated with it such as
starting and ending time, crowd participants, topics, tweets,
location data, etc. To effectively organize these properties to assist quick
and convenient retrieval by the user, we consider these two formats: timeline
and list. For both view panels, these two formats are included but sized
unequally. The size is adjustable(in the option panel) according to the user's
need. Generally, ``timeline'' is more suitable for overview a large number of
crowds while ``list'' is better for investigating details in a smaller set of crowds. We
also provide several filtering options for both timeline and list format in the
option panel. Some detailed components in these three panels are listed below.

\begin{itemize}
				\item Timeline format displays the evolution of each crowd.
        First of all, a crowd is shown as a line from the starting time
        to the ending time. The size of the participants over time is
        indicated by color(e.g., small-large-medium $\longrightarrow$
        green-red-blue). The top three keywords that describe the topic of
        the crowd are displayed explicitly on the timeline along with
        the crowd line. Extra information about the crowd can be viewed
        in the pop up box when the user clicks on the crowd line.

        \item List format displays each crowd with some specific
        sorting order. The default sorting order is by the starting
        time. Some other available sorting functions include the
        ending time, the size of crowds and the ranging time. In the
        list format, crowds are displayed explicitly in three columns:
        time period, participants and size of the crowds. If the crowd is clicked, it will show the list
        of tweets and other detailed information in a slide down window
        form.
%    \item \textit{Global View Panel} : The global view shows the global crowds
%    in different format. When a crowded is marked by the user, a flag will be
%    placed in front of each crowd item in each format.
%
%    \begin{itemize}
%        \item Timeline format displays the evolution of each crowd.
%        First of all, a crowd is shown as a line from the starting time
%        to the ending time. The size of the participants over time is
%        indicated by color(e.g., small-large-medium $\longrightarrow$
%        green-red-blue). The top three keywords that describe the topic of
%        the crowd are displayed explicitly on the timeline along with
%        the crowd line. Extra information about the crowd can be viewed
%        in the pop up box when the user clicks on the crowd line.
%        \item List format displays each crowd with some specific
%        sorting order. The default sorting order is by the starting
%        time. Some other available sorting functions include the
%        ending time, the size of crowds and the ranging time. In the
%        list format, crowds are displayed explicitly in three columns:
%        time period, participants and size of the crowds. If the crowd is clicked, it will show the list
%        of tweets and other detailed information in a slide down window
%        form.
%    \end{itemize}
%
%    \item \textit{Personal Workspace Panel} : Similar as the Global View Panel
%    but with only the set of crowds marked by the user in the Global View
%    Panel.
%    \item \textit{Filter Option Panel} : This panel explicitly displays a set of
%    the most frequently used filtering options such as search and timeline scaling.
%    We also provide the user with flexibility to adjust the default
%    settings we provided such as the primary display format in the View
%    Panel, list sorting function and time period filtering. Other filtering
%    options are hidden and can be expanded with a click on the right bottom corner
%    of the Panel.
\end{itemize}

@@

\begin{figure}
\centering
\epsfig{file=img/TimelineView.eps, width= 250pt }
\caption{Timeline View}
\label{fig:Timeline View}
\end{figure}

\begin{figure}
\centering
\epsfig{file=img/CrowdViewInTimeline.eps, width= 250pt }
\caption{Crowd View In Timeline}
\label{fig:CrowdViewInTimeline}
\end{figure}

We apply the Simile Timeline library which is developed by MIT's Computer
Science and Artificial Intelligence Laboratory. The timeline as shown in figure \ref{fig:TimelineView} shows all of the
crowds at a given time span.  The timeline allows the analyist to zoom in on a
specific time, and move forward and backward thorough time.  The visualization
shows how long the crowd lasts, and the size of the crowd. We may make the
crowd taller or shorter based on the size of the crowd.  We will also display a
few keywords from each crowd. After a crowd in the timeline is clicked, a pop up ``Crowd View'' window will show the detailed information of this particular crowd (Figure \ref{}).

@@

\begin{figure}
\centering
\epsfig{file=img/ListView.eps, width= 250pt }
\caption{Overall List View}
\label{fig:ListView}
\end{figure}

The list view as shown in Figure \ref{fig:ListView} requires a dynamic table in which it displays as many rows as the amount of crowds returned by the API. Concretely, we issue a jQuery for all the available crowds in the database. The javascript helps to create the dynamic table which includes the following columns: Period, Users and size of the crowd.Once a row of crowd is clicked, a slide down box with detail information(crowd user network, tweets) will be shown below. There are three types of information available for users to choose from: Network, Tweets and Graph and a ``star'' mark.

Each crowd has a star-feature attached to it which can be used by the user to mark his favourite crowds.This feature is present in the detailed view of the crowd which is activated as said earlier by selecting the row of a crowd.This is used to rearrange the list of crowds with the starred crowds appearing at the top whenever the user comes back to the list view.The user can mark any crowd as starred or unstar the ones that are already starred at any point of time.

@@

\begin{figure}
\centering
\epsfig{file=img/Search.eps, width= 250pt }
\caption{Search}
\label{fig:Search}
\end{figure}
In the search function of the system, we provide a main search box in which 
users can type a textual query to search for crowds which contains the query.
Besides, users can also click the link of advanced search, so that they can 
choose options of words, time period of crowd, size of crowd, presentation ways,
and results they would like to see per page. The layout is shown in figure \ref{fig:Search}. We maintain indices for each kind
of queries in the MongoDB database, so that we can efficiently return the results
to users. Whenever a query is issued, the systems send a HTTP GET request to the
backend, and the server would return the corresponding search results.

@@

\subsubsection{Crowd View}

\begin{figure}
\centering
\epsfig{file=img/NetworkInList.eps, width= 250pt }
\caption{Network View in List}
\label{fig:NetworkInList}
\end{figure}

\begin{figure}
\centering
\epsfig{file=img/TweetsInList.eps, width= 250pt }
\caption{Tweets View in List}
\label{fig:TweetInList}
\end{figure}

\begin{figure}
\centering
\epsfig{file=img/GraphInList.eps, width= 250pt }
\caption{Graph View in List}
\label{fig:GraphInList}
\end{figure}
When an analyst clicks a crowd in the list, timeline, or map view, we show an
expanded view of the crowd. This is a form of progressive disclosure, where we
give the analyst more information as they need it.

The default view is the Network information as shown in figure \ref{fig:NetworkInList} where nodes represent users, and edges represent the tweets. The network graph show the relationship of the users involved in this particular crowd based on the tweets mentioning activities. A thicker edge between two users indicate a tighter mentioning action between them. We plan to add the ability to drill down even more.  When the analyst clicks on a node, we can give the analyst more information about the user that was clicked on. When the analyst clicks on an edge, we can show the conversation between two users.
 %Jeff, would you like to talk more about the network%

In the Tweets tab we can see a set of tweets in this crowd like in figure \ref{fig:TweetInList}. In order to provide users a cleaner page view, we restrict 5 tweets per page to show in the slide down box and thus, a multiple page navigation is possible. Users can click on the ``Next 5 tweets'' if it is available.

The Graph view shows the activeness of the crowds in an hourly time basis. Figure \ref{fig:GraphInList} gives a crowd graph example. We can see how a crowd start to engage, develop and die over time.

@@

Finally, we want to improve the timeline component so it can support zoom in and zoom out functionality for better scaling flexibility. For example, crowds within the same day are grouped in the default view. The users might want to zoom in and see a hourly-display of crowds in each day or zoom out to browse crowds in each of the 12 months of a year.
